---
title: "Diversity of partitions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Diversity-of-partitions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(QCAcluster)
library(knitr) # nicer html tables
```

For illustration, we use data from [Schwarz 2016](https://doi.org/10.1080/07036337.2016.1203309). The data structure is an unbalanced panel with eight countries, ten years and 74 observations in total. `partition_div()` requires as input only parameters for the calculation of the pooled solution plus identifiers for the units (`units`) and periods (`time`).
```{r}
# load data (see data description for details)
data(Schwarz2016)
Schwarz_div <- partition_div(Schwarz2016, 
                             units = "country", time = "year", 
                             cond = c("poltrans", "ecotrans", "reform",
                                      "conflict", "attention"), 
                             out = "enlarge", 1, 0.8)
kable(Schwarz_div)
```

The dataframe shows how the cases are distributed across truth table rows. The information is presented in absolute numbers and relative terms and for all truth table rows and the subset of consistent and inconsistent rows.