---
title: "Weight of partitions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Weight of partitions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = F}
library(QCAcluster)
library(knitr) # nicer html tables
```

### Conservative and parsimonious solution
We use the data from [Thiem (2011)](https://doi.org/10.1017/S1755773910000251) for illustrating how the function `wop()` calculates the weights of partitions. The weight of a partition is defined on the level of individual models and can be calculated for the *consistency* and *coverage* value of a model derived for the pooled data. The weight of a partition for the consistency value of the pooled solution is calculated by applying the consistency formula only to the cases that belong to a partition. The function takes a disaggregated perspective on the weights of partitions by calculating their *absolute* weights separately for the numerator and denominator of a formula. This allows one to use the output of the function to calculate their *relative* weights separately for the numerator and denominator of the consistency or coverage formula (see below).

The arguments of the functions are:

- `n_cut`: Frequency threshold for pooled data
- `incl_cut`: Inclusion threshold (a.k.a. consistency threshold) for pooled data
- `solution` (only for `partition_min()`): Either `C` for conservative solution (a.k.a. complex solution) or `P` for parsimonious solution
- `BE_cons` and `WI_cons`: Inclusion thresholds for cross sections and time series. The length of the numeric vector should equal the number of units and time series.
- `BE_ncut` and `WI_ncut`: Frequency thresholds for the cross sections and time series. The length of the numeric vector should equal the number of units and time series.
```{r}
# loading data
data(Thiem2011)
# calculating weight of partitions
Thiem_wop_pars <- wop(
  dataset = Thiem2011,
  units = "country", time = "year",
  cond = c("fedismfs", "homogtyfs", "powdifffs", "comptvnsfs", 
           "pubsupfs", "ecodpcefs"),
  out = "memberfs",
  n_cut = 6, incl_cut = 0.8,
  solution = "P",
  BE_cons = c(0.9, 0.8, 0.7, 0.8, 0.85, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8),
  BE_ncut = rep(1, 11),
  WI_cons = c(0.75, 0.8, 0.9, 0.8, 0.85, rep(0.75, 10)),
  WI_ncut = rep(1, 15))
# result
kable(Thiem_wop_pars)
```

### Intermediate solution
The weight of partitions for intermediate solutions is produced with `wop_inter()`. We use data from [Schwarz 2016](https://doi.org/10.1080/07036337.2016.1203309) to illustrate the function.
```{r}
# loading data
data(Schwarz2016)
# calculating weight of partitions
Schwarz_wop_inter <- partition_min_inter(
  Schwarz2016,
  units = "country", time = "year",
  cond = c("poltrans", "ecotrans", "reform", "conflict", "attention"),
  out = "enlarge",
  n_cut = 1, incl_cut = 0.8,
  intermediate = c("1", "1", "1", "1", "1"))
# result
kable(Schwarz_wop_inter)
```

